The variability of Betelgeuse explained by surface convection\thanks{Based on observations obtained at the T\'elescope Bernard Lyot (TBL) at Observatoire du Pic du Midi, CNRS/INSU and Universit\'e de Toulouse, France.}

### 2024-05-17 main.tex
fix tense

 In Fig.\ref{Lomb Scargle AAVSO}, we computed the periodogram from that light curve of Betelgeuse (blue line), alongside the periodogram computed exclusively with AAVSO observations made less than 2 days from our observation dates of the TBL (orange line). 
 For the periodogram since 1990, we binned the observations with an interval of 10 days, as Betelgeuse has been more observed in the 21st century \citep{kiss_variability_2006}. This periodogram  recovers the 400 d period and also a period close to 200 d. Other visible peaks are rather 
 due to the windowing effect.   However, when focusing on the periodogram derived from the light curve corresponding to the TBL observation dates, we fail to retrieve the periods mentioned in the literature. The periodicities found in the TBL observations 
 gain validity through this comparison: they were evident in the TBL data, but barely recovered in the AAVSO data when pruned to the same observing dates. We can anticipated that extended spectropolarimetric observations 
 of Betelgeuse will make these periodicities seen in linear polarization, and arising from convective structures, clearer and clearer.

>>>>

 In Fig.\ref{Lomb Scargle AAVSO}, we computed the periodogram from that light curve of Betelgeuse (blue line), alongside the periodogram computed exclusively with AAVSO observations made less than 2 days from our observation dates of the TBL (orange line). 
 For the periodogram since 1990, we binned the observations with an interval of 10 days, as Betelgeuse has been more observed in the 21st century \citep{kiss_variability_2006}. This periodogram  recovers the 400 d period and also a period close to 200 d. Other visible peaks are rather 
 due to the windowing effect.   However, when focusing on the periodogram derived from the light curve corresponding to the TBL observation dates, we fail to retrieve the periods mentioned in the literature. The periodicities found in the TBL observations 
 gain validity through this comparison: they were evident in the TBL data, but barely recovered in the AAVSO data when pruned to the same observing dates. We can anticipate that extended spectropolarimetric observations 
 of Betelgeuse will make these periodicities seen in linear polarization, and arising from convective structures, clearer and clearer.
